---
title: "Case Study 2"
author: "Gabriel barbosa"
date: "2023-06-28"
output: html_document
---
## Introduction
**Desired outcome of the case study.**
In this case study we will look at the movies data set from MovieLens.
It contains data about users and how they rate movies.
The idea is to analyze the data set, make conjectures, support or refute those conjectures with data, and tell a story about the data!

## Importing the Data
```{r, echo=T, eval=F}
movielens = 'https://raw.githubusercontent.com/dnchari/DS501_MovieLens/master/Results/unifiedMLDataMulti.csv'
mlData = read.csv(movielens)
```

## Report some basic details of the data you collected. For example:**
- How many ratings of 4.5 or over were given?
```{r}
#
all_rating = mlData$rating

#
above_threshold = all_rating >= 4.5

#
rating = sum(above_threshold)

#
rating

```
- How many ratings of 4.5 or over were given by specifically men or women?
```{r}
#
all_rating = table(mlData$rating >= 4.5, mlData$gender)

#
dimnames(all_rating) <- list(
  Rating = c("Below 4.5", "Above or Equal to 4.5"),
  Gender = c("Female", "Male")
)

#
all_rating
```
- How many movies have an average rating over 4.5 overall?
```{r}

avg_rating = aggregate(rating ~ movie_title, data = mlData, FUN = mean)

filtered_avg_rating <- avg_rating[avg_rating$rating >= 4.5, ]

# Convert average ratings to formatted strings
formatted_ratings <- sprintf("%.2f", filtered_avg_rating$rating)

# Create the table with movie titles and average ratings
table_data <- data.frame(movie_title = filtered_avg_rating$movie_title, average_rating = formatted_ratings)

# Display the table
print(table_data)

```
- How many movies have an average rating over 4.5 overall among only men and only women?
```{r}

```


- How many movies have an median rating over 4.5 among men over age 30? How about women over age 30?
- What are the ten most popular movies?
    + Choose what you consider to be a reasonable definition of "popular".
    + Be perpared to defend this choice.