---
title: "Case Study 2"
author: "Gabriel barbosa"
date: "2023-06-28"
output:
  html_document: default
  pdf_document: default
---
## Introduction
**Desired outcome of the case study.**
In this case study we will look at the movies data set from MovieLens.
It contains data about users and how they rate movies.
The idea is to analyze the data set, make conjectures, support or refute those conjectures with data, and tell a story about the data!

## Report some basic details of the data you collected. For example:**
How many ratings of 4.5 or over were given?
```{r}
movielens = 'https://raw.githubusercontent.com/dnchari/DS501_MovieLens/master/Results/unifiedMLDataMulti.csv'
mlData = read.csv(movielens)

# Pulling only the column I need for this problem
all_rating = mlData$rating

# Filter the rating column by all ratings above 4.5
above_threshold = all_rating >= 4.5

# Count how many ratings are above 4.5
rating = sum(above_threshold)

# Total number of ratings above 4.5
cat("The total number of ratings above 4.5 is:", rating, "\n")

```
How many ratings of 4.5 or over were given by specifically men or women?
```{r}
# Filter the dataset by the columns we need
all_rating = table(mlData$rating >= 4.5, mlData$gender)

# Rename the dimensions to reflect the data
dimnames(all_rating) = list(
  Rating = c("Below 4.5", "Above or Equal to 4.5"),
  Gender = c("Female", "Male")
)

# Total number of ratings above and below 4.5 separated by gender
all_rating
```

How many movies have an average rating over 4.5 overall?
```{r}
# Filter the data set by the columns we need and take the mean of the rating using the FUN function
avg_rating = aggregate(rating ~ movie_title, data = mlData, FUN = mean)

# Filter out any ratings below 4.5
filtered_avg_rating = sum(avg_rating$rating > 4.5)

# Display results in string format
cat("The total number of movies with an average rating above 4.5 is: ", filtered_avg_rating, "\n")
```
How many movies have an average rating over 4.5 overall among only men and only women?
```{r}
# Separate our data by gender
men_data = mlData[mlData$gender == 'M', ]
women_data = mlData[mlData$gender == 'F', ]

# Take the average of our movies by movie title for men and women separately
men_avg_rating = aggregate(rating ~ movie_title, data = men_data, FUN = mean)
women_avg_rating = aggregate(rating ~ movie_title, data = women_data, FUN = mean)

# Sum up the number of movies with an average rating above 4.5
men_high_ratings_count = sum(men_avg_rating$rating >= 4.5)
women_high_ratings_count= sum(women_avg_rating$rating >= 4.5)

# Display results in string format
cat("The total number of movies with an average rating of 4.5 or above among men is: ", men_high_ratings_count, "\n")
cat("The total number of movies with an average rating of 4.5 or above among women is: ", women_high_ratings_count, "\n")

```
How many movies have a median rating over 4.5 among men over age 30? How about women over age 30?
```{r}
# Separate our data by gender and remove anybody 30 or younger
men_data = mlData[mlData$gender == 'M' & mlData$age > 30, ]
women_data = mlData[mlData$gender == 'F' & mlData$age > 30, ]

# Take the median of our movies by movie title for men and women separately
men_over_30_median = aggregate(rating ~ movie_title, data = men_data, FUN = median)
women_over_30_median = aggregate(rating ~ movie_title, data = women_data, FUN = median)

# Sum up the number of movies with a median over 4.5
men_high_median = sum(men_over_30_median$rating > 4.5)
women_high_median = sum(women_over_30_median$rating > 4.5)

# Display results in string formet
cat("The number of movies with a median rating over 4.5 among men over 30 is: ", men_high_median, "\n")
cat("The number of movies with a median rating over 4.5 among women over 30 is: ", women_high_median, "\n")

```
What are the ten most popular movies? Defining popular as the 10 movies with the most 5 start ratings. 
```{r}
library(dplyr)

# Count the number of ratings per movie
rating_counts = table(mlData$movie_title)

# Sort the rating counts in descending order
sorted_counts = sort(rating_counts, decreasing = TRUE)

# Filter movies with rating counts greater than 250
filtered_movies = names(sorted_counts[sorted_counts > 250])

# Filter the data frame by movies with rating counts greater than 250
df_filtered = mlData[mlData$movie_title %in% filtered_movies, ]

# Filter the ratings to include only ratings of 5
filtered_ratings = df_filtered[df_filtered$rating == 5, ]

# Calculate the total number of ratings of 5 for each movie
# Sort by descending order of total ratings of 5
rating_counts = filtered_ratings %>%
  group_by(movie_title) %>%
  summarize(total_ratings_5 = sum(rating == 5)) %>%
  arrange(desc(total_ratings_5))

# Select the top 5 movies with highest total ratings of 5
top_5_movies = head(rating_counts, 5)

# Print the top 5 movies
print(top_5_movies)


```

## Problem 2: Expand our investigation to histograms

Plot a histogram of the ratings of all movies
```{r}
library('ggplot2')

hist(mlData$rating, breaks = seq(0, 5, by = 0.5), col = 'blue', xlab = 'Rating', ylab = 'Frequency', main = 'Histogram of Movie Ratings')
```

Plot a histogram for the number of ratings each movie received (With outliers):
```{r}
# Filter the data set by the columns we need
data = mlData[, c("movie_title", "rating")]

# Count the number of ratings per movie
rating_counts = table(data$movie_title)

# Create a histogram to visualize the distribution of rating counts
hist(rating_counts,
     xlab = "Number of Ratings",
     ylab = "Frequency",
     main = "Distribution of Rating Counts",
     col = "navy"
)

```

Plot a histogram for the number of ratings each movie received (Without outliers):
```{r}

# Filter the data set by the columns we need
data = mlData[, c("movie_title", "rating")]

# Count the number of ratings per movie
rating_counts = table(data$movie_title)

# Define outlier fences based on the interquartile range (IQR)
Q1 = quantile(rating_counts, 0.20)
Q3 = quantile(rating_counts, 0.80)
IQR = Q3 - Q1
lower_fence = Q1 - 1.5 * IQR
upper_fence = Q3 + 1.5 * IQR

# Exclude outliers from rating counts
filtered_rating_counts = rating_counts[rating_counts >= lower_fence & rating_counts <= upper_fence]

# Create a histogram to visualize the distribution of rating counts without outliers
hist(filtered_rating_counts,
     xlab = "Number of Ratings",
     ylab = "Frequency",
     main = "Distribution of Rating Counts (Excluding Outliers)",
     las = 1,
     col = "navy"
)


```

Plot a histogram of the average rating for each movie.
```{r}

# Filter the data set by the columns we need
data = mlData[, c("movie_title", "rating")]

# Take the average of the movie ratings
avg_rating = aggregate(rating ~ movie_title, data = data, FUN = mean)

# Create a histogram to visualize the distribution of average ratings
hist(avg_rating$rating,
     xlab = "Average Rating",
     ylab = "Frequency",
     main = "Distribution of Average Ratings",
     las = 1,
     col = "navy"
)

```

Plot a histogram of the average rating for movies which are rated more than 100 times.
```{r}
# Filter the data set by the columns we need
data = mlData[, c("movie_title", "rating")]

# Count the number of ratings per movie
rating_counts = table(data$movie_title)

# Filter movies with rating counts greater than 100
filtered_movies = names(rating_counts[rating_counts > 100])

# Filter the data frame by movies with rating counts greater than 100
df_filtered = data[data$movie_title %in% filtered_movies, ]

# Calculate the average rating for each movie
avg_rating = aggregate(rating ~ movie_title, data = df_filtered, FUN = mean)

# Create a histogram of the average rating for movies with rating counts > 100
hist(avg_rating$rating,
     xlab = "Average Rating",
     ylab = "Frequency",
     main = "Histogram of Average Rating (Movies with >100 Ratings)",
     las = 1,
     col = "navy"
)

```
What do you observe about the tails of the histogram where you use all the movies versus the one where you only use movies rated more than 100 times?

- Although the highest average rating of 5 and the lower ratings below have been removed, the data still seems to       clump between 3-4 and narrow down towards the edge of the histogram. Including all of the movies outline the effect   of the outliers in our data.
  
Which highly rated movies would you trust are actually good? Those rated more than 100 times or those rated less than 100 times?

- I would prefer to watch a decently rated movie with a large sample size used to obtain that rating over a movie with a great rating and small sample size. By having a larger sample size, I believe there is more variation in the     movie preferences of the people, which represents the general public more accurately. Lowering the sample size means limiting the variation in preference and not representing the different opinions equally. 
  
Conjecture

- I wanted to see if there was any correlation between the average rating of the movies and the age of the person rating the movie. The scatter plot shows that the older participants gave slightly higher ratings on average. 
```{r}

# Filter the data set by the columns we need
data = mlData[, c("movie_title", "rating", "age")]

# Calculate the average rating for each age category
avg_rating = aggregate(rating ~ age, data = data, FUN = mean)

# Fit a linear regression model
lm_model = lm(rating ~ age, data = avg_rating)

# Create a scatter plot of the average rating based on age
plot(avg_rating$age, avg_rating$rating,
     xlab = "Age",
     ylab = "Average Rating",
     main = "Average Rating by Age",
     col = "navy",
     pch = 16
)

# Add a line showing the trend
abline(lm_model, col = "turquoise")

```

- I noticed that the occupation with the most votes was that of student with over 47000 votes. I want to dive deeper into this demographic.
```{r}
# Filter the data set by the columns we need
data = mlData[, c("movie_title", "rating", "occupation")]

# Calculate the total number of ratings for each occupation category
rating_counts = table(data$occupation)
rating_counts
```

- First, I want to see the movies the students gave the most 5 stars to.
```{r}
library(dplyr)

# Filter the data set for students
data = mlData[mlData$occupation == "student", ]

# Filter the ratings to include only 5-star ratings
filtered_ratings = data[data$rating == 5, ]

# Calculate the total number of 5-star ratings per movie
rating_counts = as.data.frame(table(filtered_ratings$movie_title))
rating_counts = rating_counts[order(rating_counts$Freq, decreasing = TRUE), ]

# Filter the rating_counts dataframe to only include the top 10 movies
top_10_years = head(rating_counts, 10)

# Print the total number of 5-star ratings per movie for the top 10 movies
print(top_10_years)

```

- While looking at this list I noticed the year of the movie was included with the movie title within the movie_title column. What I'm going to do next is unlist the words within this column and use the numbers to separate the 5 star votes by year instead of by movie. 
```{r}

library(stringi)
library(ggplot2)

# Filter the data set for students
data = mlData[mlData$occupation == "student", ]

# Filter the ratings to include only 5-star ratings
filtered_ratings = data[data$rating == 5, ]

# Initialize an empty vector to store the extracted years
years = c()

# Loop through each movie_title
for (title in filtered_ratings$movie_title) {
  # Remove non-ASCII characters
  cleaned_title = stri_trans_general(title, "Latin-ASCII")
  
  # Match the regular expression pattern
  match = regexpr("\\(([0-9]{4})\\)", cleaned_title)
  
  # Check if there is a valid match
  if (match > 0) {
    # Extract the year from the matched substring
    year = substr(cleaned_title, match + 1, match + 4)
    
    # Append the extracted year to the vector
    years = c(years, year)
  }
}

# Create a data frame with the year counts
year_counts = as.data.frame(table(years))

# Rename the columns for clarity
colnames(year_counts) = c("Year", "Count")

# Order the data frame by count in decreasing order
year_counts = year_counts[order(year_counts$Count, decreasing = TRUE), ]

# Filter the year_counts data frame to include only the last 10 years
top_10_years = head(year_counts, 10)

# Order the top 10 years by Count in decreasing order
top_10_years = top_10_years[order(top_10_years$Count, decreasing = TRUE), ]

# Create a bar graph of the last 10 years' ratings with vertical x-axis labels
ggplot(top_10_years, aes(x = Year, y = Count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Year", y = "Total Ratings", title = "Total Ratings in the Top 10 Years") +
  scale_x_discrete(limits = top_10_years$Year)




```

- Instead of taking the number of rating counts by movie I chose to separate it by year. I wanted to experiment with pulling apart the strings in the movie_title column and using the year to separate the movies.The year with the most 5-star ratings from the top 10 5-star only rated movies for students turned out be 1996. The movies this year must have been very good!

## Problem 3: Correlation: Men versus women

Make a scatter plot of men versus women and their mean rating for every movie.
```{r}
library(ggplot2)

# Separate our data by gender
men_data = mlData[mlData$gender == 'M', ]
women_data = mlData[mlData$gender == 'F', ]

# Take the average of our movies by movie title for men and women separately
men_avg_rating = aggregate(rating ~ movie_title, data = men_data, FUN = mean)
women_avg_rating = aggregate(rating ~ movie_title, data = women_data, FUN = mean)

# Create a combined data frame with average ratings for men and women
combined_avg_ratings = merge(men_avg_rating, women_avg_rating, by = "movie_title", suffixes = c("_men", "_women"))

# Create the scatterplot
ggplot(combined_avg_ratings, col = "navy", aes(x = rating_men, y = rating_women)) +
  geom_point() +
  labs(x = "Mean Rating - Men", y = "Mean Rating - Women", title = "Mean Ratings: Men vs Women") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")  # Add diagonal line for reference

```

Make a scatter plot of men versus women and their mean rating for movies rated more than 200 times.
```{r}
library(ggplot2)

# Separate our data by gender
men_data = mlData[mlData$gender == 'M', ]
women_data = mlData[mlData$gender == 'F', ]

# Take the average of our movies by movie title for men and women separately
men_avg_rating = aggregate(rating ~ movie_title, data = men_data, FUN = mean)
women_avg_rating = aggregate(rating ~ movie_title, data = women_data, FUN = mean)

# Create a combined data frame with average ratings for men and women
combined_avg_ratings = merge(men_avg_rating, women_avg_rating, by = "movie_title", suffixes = c("_men", "_women"))

# Filter movies with rating counts greater than 2000
rating_counts = table(mlData$movie_title)
filtered_movies = combined_avg_ratings[combined_avg_ratings$movie_title %in% names(rating_counts[rating_counts > 200]), ]

# Create the scatterplot
ggplot(filtered_movies, aes(x = rating_men, y = rating_women)) +
  geom_point() +
  labs(x = "Mean Rating - Men", y = "Mean Rating - Women", title = "Mean Ratings: Men vs Women") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")  # Add diagonal line for reference


```

Compute the correlation coefficent between the ratings of men and women.
```{r}
library(ggplot2)

# Separate our data by gender
men_data = mlData[mlData$gender == 'M', ]
women_data = mlData[mlData$gender == 'F', ]

# Take the average of our movies by movie title for men and women separately
men_avg_rating = aggregate(rating ~ movie_title, data = men_data, FUN = mean)
women_avg_rating = aggregate(rating ~ movie_title, data = women_data, FUN = mean)

# Create a combined data frame with average ratings for men and women
combined_avg_ratings = merge(men_avg_rating, women_avg_rating, by = "movie_title", suffixes = c("_men", "_women"))

# Filter movies with rating counts greater than 100
rating_counts = table(mlData$movie_title)
filtered_movies = combined_avg_ratings[combined_avg_ratings$movie_title %in% names(rating_counts[rating_counts > 100]), ]

# Calculate the correlation coefficient
correlation_coefficient = cor(filtered_movies$rating_men, filtered_movies$rating_women)

# Create the scatterplot
ggplot(filtered_movies, aes(x = rating_men, y = rating_women)) +
  geom_point() +
  labs(x = "Mean Rating - Men", y = "Mean Rating - Women", title = "Mean Ratings: Men vs Women") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +  # Add diagonal line for reference
  annotate("text", x = max(filtered_movies$rating_men), y = min(filtered_movies$rating_women),
           label = paste("Correlation:", round(correlation_coefficient, 2)), hjust = 1, vjust = -1)  # Add correlation coefficient label

```

What do you observe?

- The correlation coefficient is positive, meaning the average rating for men and women go up together. There is also a relatively strong linear relationship between the two variables with a correlation of 0.79. 
  
Are the ratings similar or not? Support your answer with data!

- Below we can see that the overall average rating for men and women are very close. I believe their ratings are similar to each other. 
```{r}
men_data = mlData[mlData$gender == 'M', ]
women_data = mlData[mlData$gender == 'F', ]

men_avg_rating = mean(men_data$rating)
women_avg_rating = mean(women_data$rating)

cat("The average rating for men is: ", men_avg_rating, "\n")
cat("The average rating for women is: ", women_avg_rating, "\n")

```

Conjecture under what circumstances the rating given by one gender can be used to predict the rating given by the other gender.
- I've divided the age column into three brackets. The first is below 20, the second is between 21-40, and the third is 41 and above. The average ratings for all 3 brackets are very close, with women in the first two brackets averaging higher ratings overall, but men over 40 rating higher overall. 
```{r}

men_data = mlData[mlData$gender == 'M', ]
women_data = mlData[mlData$gender == 'F', ]

# Create age brackets for men
men_young_data = men_data[men_data$age < 20, ]
men_mid_age_data = men_data[men_data$age >= 20 & men_data$age <= 40, ]
men_older_data = men_data[men_data$age > 40, ]

# Create age brackets for women
women_young_data = women_data[women_data$age < 20, ]
women_mid_age_data = women_data[women_data$age >= 20 & women_data$age <= 40, ]
women_older_data = women_data[women_data$age > 40, ]

# Calculate average ratings for each age bracket and gender
men_young_avg_rating = mean(men_young_data$rating, na.rm = TRUE)
men_mid_age_avg_rating = mean(men_mid_age_data$rating, na.rm = TRUE)
men_older_avg_rating = mean(men_older_data$rating, na.rm = TRUE)

women_young_avg_rating = mean(women_young_data$rating, na.rm = TRUE)
women_mid_age_avg_rating = mean(women_mid_age_data$rating, na.rm = TRUE)
women_older_avg_rating = mean(women_older_data$rating, na.rm = TRUE)

# Print the results
cat("Average rating for men younger than 20: ", men_young_avg_rating, "\n")
cat("Average rating for men 21-40: ", men_mid_age_avg_rating, "\n")
cat("Average rating for men 41 and up: ", men_older_avg_rating, "\n\n")

cat("Average rating for women younger than 20: ", women_young_avg_rating, "\n")
cat("Average rating for women 21-40: ", women_mid_age_avg_rating, "\n")
cat("Average rating for women 41 and up: ", women_older_avg_rating, "\n")


```

- I wanted to dive a little deeper into these ratings and take a look at it by genre on top of all of the filters I applied above. 
```{r}
# Create age brackets for men
men_young_data = men_data[men_data$age < 20, ]
men_mid_age_data = men_data[men_data$age >= 20 & men_data$age <= 40, ]
men_older_data = men_data[men_data$age > 40, ]

# Create age brackets for women
women_young_data = women_data[women_data$age < 20, ]
women_mid_age_data = women_data[women_data$age >= 20 & women_data$age <= 40, ]
women_older_data = women_data[women_data$age > 40, ]

# Calculate average ratings by genre and age bracket for men
men_young_avg_rating = aggregate(rating ~ genre, data = men_young_data, FUN = mean)
men_mid_age_avg_rating = aggregate(rating ~ genre, data = men_mid_age_data, FUN = mean)
men_older_avg_rating = aggregate(rating ~ genre, data = men_older_data, FUN = mean)

# Calculate average ratings by genre and age bracket for women
women_young_avg_rating = aggregate(rating ~ genre, data = women_young_data, FUN = mean)
women_mid_age_avg_rating = aggregate(rating ~ genre, data = women_mid_age_data, FUN = mean)
women_older_avg_rating = aggregate(rating ~ genre, data = women_older_data, FUN = mean)

# Sort the average ratings in descending order
men_young_avg_rating = men_young_avg_rating[order(-men_young_avg_rating$rating), ]
men_mid_age_avg_rating = men_mid_age_avg_rating[order(-men_mid_age_avg_rating$rating), ]
men_older_avg_rating = men_older_avg_rating[order(-men_older_avg_rating$rating), ]
women_young_avg_rating = women_young_avg_rating[order(-women_young_avg_rating$rating), ]
women_mid_age_avg_rating = women_mid_age_avg_rating[order(-women_mid_age_avg_rating$rating), ]
women_older_avg_rating = women_older_avg_rating[order(-women_older_avg_rating$rating), ]

# Group the results by the top 5 highest ratings for each age bracket
men_young_top5 = men_young_avg_rating[1:5, ]
men_mid_age_top5 = men_mid_age_avg_rating[1:5, ]
men_older_top5 = men_older_avg_rating[1:5, ]
women_young_top5 = women_young_avg_rating[1:5, ]
women_mid_age_top5 = women_mid_age_avg_rating[1:5, ]
women_older_top5 = women_older_avg_rating[1:5, ]

# Print the results
cat("Top 5 average ratings for men younger than 20 by genre:\n")
print(men_young_top5)

cat("\nTop 5 average ratings for men 21-40 by genre:\n")
print(men_mid_age_top5)

cat("\nTop 5 average ratings for men 41 and up by genre:\n")
print(men_older_top5)

cat("\nTop 5 average ratings for women younger than 20 by genre:\n")
print(women_young_top5)

cat("\nTop 5 average ratings for women 21-40 by genre:\n")
print(women_mid_age_top5)

cat("\nTop 5 average ratings for women 41 and up by genre:\n")
print(women_older_top5)

```
The only genre that appears in the top 5 for all 6 age brackets is war, and it is in either first, second, or third place. I think it's fair to say that if the movie genre is war, regardless of gender, we can assume that the rating will be high. 

Conjecture
- I want to filter the average ratings by occupation to see if there are any trends there
```{r}
# Load the dplyr package
library(dplyr)

# Assuming your dataset is named 'movies'
# Use the group_by() and summarise() functions to calculate the average rating for each occupation
average_ratings = mlData %>%
  group_by(occupation) %>%
  summarise(average_rating = mean(rating, na.rm = TRUE)) %>%
  arrange(desc(average_rating))

# Print the resulting average ratings for each occupation
print(average_ratings)

```

- Excluding the none category, the occupation with the highest average ratings seems to be the lawyers. The group with the lowest ratings are the healthcare workers. Healthcare is the only occupation with an average rating below 3. let's dive a little deeper into the healthcare data by separating all of the ratings of the healthcare workers by movie genre.
```{r}

healthcare_data = mlData[mlData$occupation == 'healthcare', ]
rating_count = as.data.frame(table(healthcare_data$genre))

# Calculate percentage
rating_percentage = (rating_count$Freq / sum(rating_count$Freq)) * 100

healthcare_avg_data = aggregate(rating ~ genre, data = healthcare_data, FUN = mean)

# Create a combined table
combined_table = cbind(rating_count, rating_percentage, healthcare_avg_data)

# Sort the combined table in descending order based on count column
combined_table = combined_table[order(combined_table$Freq, decreasing = TRUE), ]

# Print the sorted combined table
print(combined_table)

# Set larger bottom margin to view labels 
par(mar = c(8, 6, 4, 2) + 0.1)  
par(mgp = c(5, 1, 0)) 

# Create the bar plot
barplot(combined_table$Freq, names.arg = combined_table$genre, 
        xlab = "Genre", ylab = "Count", main = "Count of Genres in Healthcare Data", las = 2)

# Reset the margins and mgp parameter to default
par(mar = c(5, 4, 4, 2) + 0.1)  
par(mgp = c(3, 1, 0))  


```
The first thing I notice here is that 4 genres make up over half of their ratings. Almost a quarter of their ratings are of drama movies, and this is one of their lowest scoring genres. 

I'm assuming this is a trend for all occupations. Let's find out!
```{r}

rating_count = as.data.frame(table(mlData$genre))

# Calculate percentage
rating_percentage = (rating_count$Freq / sum(rating_count$Freq)) * 100

healthcare_avg_data = aggregate(rating ~ genre, data = healthcare_data, FUN = mean)

# Create a combined table
combined_table = cbind(rating_count, rating_percentage, healthcare_avg_data)

# Sort the combined table in descending order based on count column
combined_table = combined_table[order(combined_table$Freq, decreasing = TRUE), ]

# Print the sorted combined table
print(combined_table)

# Set larger bottom margin to view labels 
par(mar = c(8, 6, 4, 2) + 0.1)  
par(mgp = c(5, 1, 0)) 

# Create the bar plot
barplot(combined_table$Freq, names.arg = combined_table$genre, 
        xlab = "Genre", ylab = "Count", main = "Count of Genres", las = 2)

# Reset the margins and mgp parameter to default
par(mar = c(5, 4, 4, 2) + 0.1)  
par(mgp = c(3, 1, 0))

```

Just as I suspected! I don't think this data would be useful if we were concerned with the genre of the movie and not just the overall total movie average. Like with the question above about wanting a large sample size over a small size, I would want all genres to be equally represented as well. I wonder if the data would look the same if we had obtained an equal number of ratings for each genre.

## Problem 4: Open Ended Question: Business Intelligence
Do any of your conjectures in Problems 1, 2, and 3 provide insights that a movie company might be interested in?

- I think the conclusion I came to about the war movie genre was interesting. It seems to be a favorite for everybody. This information could be used to determine what type of movie to put their money into for the highest value/return.
  
Propose a business question that you think this data can answer.

- What movie from the 70s/80s/90s would perform best if we were to remake it? I'm sure Disney goes through a process like this to determine which of their classics they should remake. 
  
Suppose you are a Data Scientist at a movie company. Convince your boss that your conjecture is correct!

- I believe my conjecture is correct because the correlation coefficient of the ratings was moderately high at 0.79. This proves that the data is linear.  

